Near Optimal Behavior with Approximate State Abstraction

### 2016-02-04 paper/results_discussion.tex

\section{Approximate Abstraction on Example Domains}
%Explanation of what abstraction is used
We run experiments on aggregation functions the $\ep{Q^*}$ abstraction. For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\ep{Q^*}$ criteria. The order in which ground states are selected and then greedily added is randomized so there is randomization across trials. Every ground state is equally weighted in its abstract state.

>>>>

\section{Approximate Abstraction on Example Domains}
%Explanation of what abstraction is used
We run experiments on aggregation functions the $\epQ$ abstraction. For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\epQ$ criteria. The order in which ground states are selected and then greedily added is randomized so there is randomization across trials. Every ground state is equally weighted in its abstract state.
